Contracts for Contracts

### 2022-11-21 paper.tex
more random thoughts

%% Title information
\title[Short Title]{Contracts for Contracts}         %% [Short Title] is optional;
%\title[Short Title]{Contracts meet Contracts}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Adding Higher-Order Contracts for Smart Contract}                     %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

reliability and security of smart contract programs

contracts enforce properties/check invariants at runtime
  Effiel, Design by Contract
  %https://se.inf.ethz.ch/~meyer/publications/old/dbc_chapter.pdf
  Racket, higher-order contracts

%https://docs.soliditylang.org/en/v0.8.17/control-structures.html?highlight=require#panic-via-assert-and-error-via-require
smart contracts use callback, need for higher-order contract,

One of the most adopted smart contract language Solidity indeed provides
linguistic mechanisms such as @require@ and @assert@ to enforce first-order
properties, however they does not deal with function values.
\todo{need double check}

Static verification cannot completely address the issue here since
transaction developers are oblivious to the user-provided callback.

>>>>

%% Title information
\title[Short Title]{Contracts for Contracts}         %% [Short Title] is optional;
%\title[Short Title]{Contracts meet Contracts}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Adding Higher-Order Contracts for Smart Contracts}                     %% \subtitle is optional
\subtitle{Expressive Assertion Monitoring System for Safer Smart Contracts}                     %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

\todo{exciting intro of smart contract}

Building trustworthy and secure smart contract programs requires solid
understanding and reliable enforcement of program invariants.
\todo{why? solidity is rather flexible, unsatisfying/weaker type system,
not all invariants can be checked statically, e.g. the status of the chain}

contracts enforce properties/check invariants at runtime pioneered by the
Effiel language and the Design by Contract methodology.
  %https://se.inf.ethz.ch/~meyer/publications/old/dbc_chapter.pdf

One of the most adopted smart contract language Solidity indeed provides a
simple assertion mechanism such as @require@ to enforce properties.
However, the provided mechanism only handles first-order properties and does
not deal with function values.  \todo{GW: need double check}

Solidity supports higher-order functions (\todo{GW: does it support returning
functions?}, however, the lack of reliable means to enforce properties
for higher-order programs discourages programmers to use these powerful
abstractions. It also leads to unfortunate real-world hazards.

%https://docs.soliditylang.org/en/v0.8.17/control-structures.html?highlight=require#panic-via-assert-and-error-via-require
One \note{common} use case of higher-order functions in smart contracts is
to express callback \todo{explain how it is used}.
\todo{need for richer mechanisms to enforce invariants of HO functions}
Racket, higher-order contracts

\todo{it is hard to enforce properties when callbacks exist}
Static verification cannot completely address the issue here since
transaction developers are oblivious to the user-provided callback.
